\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Luchian Mihai} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+40731757891}{+40 731 757 891}
    $|$
    \faAt \hspace{.5pt} \href{mailto:luchiann.mihai@gmail.com}{luchiann.mihai@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/luchian-mihai}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/LuchianMihai}{GitHub}
    $|$
    %\faGlobe \hspace{.5pt} \href{https://arasgungore.github.io}{Portfolio}
    %$|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Bra%C8%99ov/@45.6525685,25.5140627,12z/data=!3m1!4b1!4m6!3m5!1s0x40b35b862aa214f1:0x6cf5f2ef54391e0f!8m2!3d45.6426802!4d25.5887252!16zL20vMGhqdGc?entry=ttu}{Brasov, Romania}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Transilvania University of Brasov}{Brasov, Romania}
      {B.Sc. in Computer Science}{Sep 2014 \textbf{--} Jun 2018}
         \resumeItemListStart
             \resumeItem{Faculty of Electrical Engineering and Computer Science, Department of Applied Electronics}
         \resumeItemListEnd

    \resumeSubheading
      {Transilvania University of Brasov}{Brasov, Romania}
      {M.Sc. in Computer Science}{Oct 2022 \textbf{--} Jun 2024 (Expected)}
         \resumeItemListStart
             \resumeItem{Faculty of Mathematics and Informatics, Department of Applied Informatics}
         \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {The Quality-Assurance Test of the ATLAS New Small Wheel Read-Out Controller ASIC}{}
      {Proceeding of Science (PoS), 081, 2019}{***}
        \resumeItemListStart
            \resumeItem{\textbf{Authors:} S. Popa, R. Coliban, \textbf{M. Luchian}, M. Ivanovici}
            \resumeItem{Undergraduate Research Assistant @ \textit{Transilvania University of Brasov}}
        \resumeItemListEnd

    \resumeSubheading
      {Clock and data signals synchronization for an FPGA-based ASIC testing setup}{}
      {2019 International Symposium on Signals, Circuits and Systems (ISSCS), 1-4, 2019}{***}
        \resumeItemListStart
            \resumeItem{\textbf{Authors:} S. Popa, \textbf{M. Luchian}, M. Ivanovici}
            \resumeItem{Undergraduate Research Assistant @ \textit{Transilvania University of Brasov}}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Bertrandt Engineering Technologies}{Bucharest, Romania}
      {Embedded Software Engineer}{Mar 2022 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Classic AUTOSAR architecture}
            \resumeItem{Developer of Basic Software modules}
            \resumeItem{Focus on COM stack and COM stack interaction}
        \resumeItemListEnd

    \resumeSubheading
      {Elektrobit Automotive}{Brasov, Romania}
      {Embedded Software Engineer}{Oct 2020 \textbf{--} Mar 2022}
        \resumeItemListStart
            \resumeItem{Classic AUTOSAR architecture}
            \resumeItem{Developer of Basic Software modules}
            \resumeItem{Focus on COM stack and COM stack interaction}
        \resumeItemListEnd

    \resumeSubheading
      {NoBug Consulting}{Brasov, Romania}
      {Internship Digital Design and Verification}{Nov 2019 \textbf{--} Feb 2020}
        \resumeItemListStart
            \resumeItem{Digital design verification using SystemVerilog using Cadence tool suite}
            \resumeItem{Focus on Universal Verification Methodology}
        \resumeItemListEnd

    \resumeSubheading
      {Transilvania University of Brasov}{Brasov, Romania}
      {Undergraduate Research Assistant}{Oct 2017 \textbf{--} Oct 2019}
        \resumeItemListStart
            \resumeItem{RO-CERN collaboration, project ``ATLAS experiment at LHC''}
            \resumeItem{Focus on Printed Circuit Boards manufacutring proccess, and layout techniques}
            \resumeItem{Redacted Bachelor's degree Thesis}
        \resumeItemListEnd

    \resumeSubheading
      {PREH}{Brasov, Romania}
      {Internship PCB Layout Designer}{Jul 2017 \textbf{--} Ocv 2017}
        \resumeItemListStart
            \resumeItem{Digital design verification using SystemVerilog using Cadence tool suite}
            \resumeItem{Focus on Universal Verification Methodology}
        \resumeItemListEnd

    \resumeSubheading
      {Siemens Industry Software}{Brasov, Romania}
      {Software Developer Intern}{Jul 2016 \textbf{--} Jul 2017}
      \resumeSubSubheading
        {Siemens Curious Minds 2016}{Jul 2016 \textbf{--} Sep 2016}
        \resumeItemListStart
          \resumeItem{Introduction to Software Development using C++}
          \resumeItem{Introduction to Software Engineering: Compilation process, Project configuration}
          \resumeItem{Introduction to Software Architecture: Design paterns, Libraries}
        \resumeItemListEnd
      \resumeSubSubheading
        {Software Developer Trainee}{Oct 2016 \textbf{--} Jul 2017}
        \resumeItemListStart
          \resumeItem{Oriented Object Programming using C++}
          \resumeItem{Introduction to relational databases}
          \resumeItem{Focus on software architecture and design patterns}
        \resumeItemListEnd

    
  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

%\section{Awards \& Achievements}
%  \vspace{2pt}
%  \resumeSubHeadingListStart
%    \small{\item{
%        \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500.} \\ \vspace{3pt}
%        
%        \textbf{KYK Outstanding Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK).} \\ \vspace{3pt}
%        
%        \textbf{Boğaziçi University Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University.} \\ \vspace{3pt}
%        
%        \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to undergraduate students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK).} \\ \vspace{3pt}
%        
%        \textbf{Duolingo English Test (DET):}{ Overall Score: 135/160} \\ \vspace{3pt}
%        
%        % \textbf{Boğaziçi University English Proficiency Test (BUEPT):}{ Achieved the highest grade A on the BUEPT grading scheme with a total score in the range of 85-100.} \\ \vspace{3pt}
%        
%        \textbf{Kocaeli Science High School Salutatorian Award:}{ Graduated as the second-highest ranked student in my class.}
%    }}
%  \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

\section{Organizations}
  \resumeSubHeadingListStart
    
     \resumeOrganizationHeading
       {Transivania's University of Brasov Racing Team \textit{``Blue Streamline''}}{Oct 2016 \textbf{--} Jul 2019}
       {Formula Student Team Member, Lead of Electronics Department}
    
   \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Power Distribution Module | PDM}}{\textit{Blue Streamline}}
          \resumeItemListStart
            \resumeItem{An Hardware / Software project devepoled as part of electronics department tasks}
            \resumeItem{Projects goal was to monitor and control power consumers present of the single-seater}
            \resumeItem{We used AT90CAN32 MCU to recive data from an CAN interface provided by AEM Infinity ECU.
                        Power management was achived using high side smart drivers manufactured by ST Electronics.}
            \resumeItem{The hardware part of the new project was developed using Altium Designer during summer internship
                        at PREH ROMANIA S.R.L. layout department. The board was routed as an 4 layer PCB.}
            \resumeItem{The software part was developed under Linux environment, using ViM as editor, CLI based workflow,
                        git for version control, build management using makefiles. 
                        During first year mastership degree an FreeRTOS was integrated on this board.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Dashboard | HMI}}{\textit{Blue Streamline}}
          \resumeItemListStart
            \resumeItem{Project goal was to monitor engine's critical parameters and ofer the single seater's driver
                        an way to interact with the engine and paddock through use of push-buttons.}
            \resumeItem{We colected data using AT90CAN32 MCU from CAN interface provided by the
                        AEM Series 2 ECU. The procesed CAN messages were sent to 7 segments display using shift registers 
                        and alphanumeric displays on 4 wire parallel interface, also the engine's RPM was displayed using LEDs.
                        Additional push-buttons were used for gear shifting, and radio communication with the paddock.
                        Same CAN interface was used to exchange data between other electronic module present inside the vehicle.}
            \resumeItem{The hardware implementation was made using Proteus EDA tool suite for the schematic, layout
                        and greber files generation.}
            \resumeItem{The software implementation was made using AtmelStudio.
                        Code/hex upload was made using usbasp progammer over ISP interface, through avrdude software
                        and AVRDUDESS GUI.}
            \resumeItem{Endproduct consisted of two-sided PCB, hand-soldered components and manual code upload, 
                        enclosed in an 3D printed case attached on the steering wheel plate.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Brake System Plausability Device | BSPD}}{\textit{Blue Streamline}}
          \resumeItemListStart
            \resumeItem{Project implemented during fisrt year mastership degree.
                        Project goal was to be compliant with the new ruleset in Formula Student competition 
                        for both electric and combustion vehicles. The new board purpose was to cut the main power supply
                        if the driver pushed both acceleration and brake pedal at the same time over an sepcific threshold and time.}
            \resumeItem{Fully analog board using LM393 and NE555 timers.}
            \resumeItem{Board developed using KiCAD tool suite.
                        Time domain (transient) simulation achived using ngspice with KiCAD integration.}
            \resumeItem{End product manufactured abroad, consisting of two-sided PCB, 
                        through hole only, hand-soldered components.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Data Aquisition and Telemetry system | DATS}}{\textit{Blue Streamline}}
          \resumeItemListStart
            \resumeItem{Project aims to provide an way to aquire and stream live data 
                        to an remote or local server and ease the data pre/post/processing using Matlab/Symulink interaction}
            \resumeItem{Project uses an Raspberry Pi Zero 2 and esp32 boards to access data streamed on CAN interfaces}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ C, C++, MySQL, Verilog, SystemVerilog, Python} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, Arduino, ROS, Simulink, LTspice, Xilinx ISE} \\ \vspace{3pt}
        
        \textbf{Languages:}{ Turkish (Native), English (Professional), German (Elementary)}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

\section{Relevant Coursework}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Major coursework:}{ Calculus I-II, Matrix Theory, Differential Equations, Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering} \\ \vspace{3pt}
        
        \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms}
    }}
  \resumeSubHeadingListEnd


%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd


%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
